### 2022-02-08 ms_body/manuscript.tex
Make Figure 7

@@

Ecological models are important tools to support and guide the
development and implementation of environmental policies and management
programs. Species distributions models (SDM's), such as the popular
MaxEnt software, are frequently used to guide conservation programmes,
predict the potential distribution of invasive species, forecast the
impacts of climate change and develop applied ecological research
(e.g.~biological control). Many applications of these models require
that SDM's are transferred in either space and/or time. However, few
studies to date have tested the transferability, and thus usefulness, of
MaxEnt models using fully independent data. Moreover, numerous authors
have raised concerns over how model complexity (controlled primarily by
feature class and regularisation multiplier settings) may affect MaxEnt
model transferability. In this paper, we evaluated the usefulness of
MaxEnt models transferred in space using a native Australian insect,
\emph{Dasineura rubiformis} Kolesik (Diptera: Cecidomyiidae) that has
been intentionally introduced as a biological control agent of the
invasive plant, \emph{Acacia mearnsii} De Wild (Fabaceae) in South
Africa. MaxEnt models were developed using native-range records only
(Australia) and projected over South Africa to identify the potential
climatic suitability for the insect, using a range of model settings
configurations. Model transferability was assessed using independent
post-release data from South Africa. Our results demonstrated that
MaxEnt scores were positively correlated with increased establishment
rates for \emph{D. rubiformis} in South Africa. However, we found that
this pattern held only when MaxEnt models were specified with
user-defined settings configurations. A MaxEnt model calibrated with
default settings was overfit to the training data, and performed poorly
when transfered in space. Our study demonstrates that MaxEnt models can
prove useful when transferred in space, however, user-optimised model
settings likely need to be used to control model complexity, and reduce
the likelihood of overfitting.

@@

Spatial autocorrelation is an important factor that may affect model
outputs. Filtering of species occurrence data may limit the inherent
biases in the data and improve model quality (Veloz, 2009). To avoid
pseudo-replication, only one occurrence record per 2.5 minute grid cell
was used for model calibration. Species occurrence datasets were thinned
using the `spThin' package (Aiello-Lammens et al., 2015), and spatial
autocorrelation analyses were performed using the `ecospat' package (Di
Cola et al., 2017).

@@

Climate data were obtained by downloading the standard set of 19
bioclimatic variables from the WorldClim ver. 1.4 database (Hijmans et
al., 2005) (data available at: www.worldclim.org/download.html). This
dataset is representative of annual and seasonal means and variation of
temperature and precipitation metrics averaged over the 1950--2000 time
period (current climate) at a 5 arc minute resolution.

@@

Five candidate MaxEnt models were developed using native-range
(Australia) training data for \emph{D. rubiformis}. The five models
differed in the feature classes and regularisation multiplier settings
used by MaxEnt to build the models. The five models were specified with
(1) default MaxEnt settings, and four optimised settings configurations
that (2) maximised performance based on AUC\textsubscript{test}, (3)
AUC\textsubscript{diff}, (4) OR\textsubscript{10} and (5) AICc (Table
S1). The AUC values for these five models ranged were ranged between
0.82 and 0.97, depending on the MaxEnt settings configuration used. As
such, all five candidate models were considered useful and had high
predictive accuracy in distinguishing between \emph{D. rubiformis}
recorded presences and background points in its native range. While
default MaxEnt settings produced the highest discriminatory power when
tested in the training area of Australia (AUC = 0.97), models calibrated
with tuned settings configurations led to less overfitting (lower
AUC\textsubscript{diff}), better omission rates (best approximated the
expectation for OR\textsubscript{10}), and more parsimonious models
(AICc) (Fig. 2).

\hypertarget{model-transferability}{%
\subsection{3.2. Model transferability}\label{model-transferability}}

When evaluated on independent testing data in South Africa, the MaxEnt
models showed relatively high, but variable, predictive accuracy,
depending on the MaxEnt settings used to calibrate the model. For all
models, the probability that \emph{D. rubiformis} was recorded at a
field site in South Africa increased with higher MaxEnt climatic
suitability scores (Fig. 3). The default MaxEnt model found no
statistically significant relationship between MaxEnt climatic
suitability scores and the probability of \emph{D. rubiformis}
establishment in South Africa (Table. 1), and displayed low power to
discriminate between sites where \emph{D. rubiformis} had established or
not (AUC: 0.64 \(\pm\) 0.01) (Fig. 4). In contrast, the four models
calibrated using optimised model settings configurations all
demonstrated a statistically significant positive relationship between
MaxEnt suitability scores and the probability of \emph{D. rubiformis}
establishment in South Africa (Table. 1). All four tuned models
displayed high power to discriminate between sites where \emph{D.
rubiformis} had established or not (AUC: 0.83 - 0.84) than the MaxEnt
model calibrated with default settings (AUC: 0.64 \(\pm\) 0.01) (Fig.
4). The predicted climatic suitability for \emph{D. rubiformis} across
South Africa varied depending on the MaxEnt settings used to calibrate
the model (Fig. 5). Default MaxEnt settings yielded higher climatic
suitability estimates for \emph{D. rubiformis} than the other MaxEnt
models with tuned model settings, notably in regions where \emph{D.
rubiformis} is absent (e.g.~the north-west coastal region bordering
Namibia).

Despite the high performance of the MaxEnt models when transferred in
space, MESS maps indicated that the MaxEnt models were extrapolating
climatic suitability scores for \emph{D. rubiformis} over the vast
majority of South Africa (Fig. S1). Indeed, 54 of the 78 field sites
surveyed for \emph{D. rubiformis} in South Africa occur in geographic
regions where the MaxEnt models were extrapolating. \emph{Dasineura
rubiformis} established at 23 of 24 sites in interpolation (96\%), while
it established at 44 of 54 sites in extrapolation (82\%) (Fig. 6). We
found no evidence that a site being in extrapolation/interpolation was a
statistically significant predictor of \emph{D. rubiformis}
establishment in South Africa (X\textsubscript{2} = 3.40, d.f = 1,
\emph{P} = 0.07). Moreover, classifying sites as being in
extrapolation/interpolation yielded lower power to discriminate to
discriminate between sites where \emph{D. rubiformis} had established or
not (AUC: 0.67 \(\pm\) 0.02) than all of the MaxEnt models, barring the
model with default settings.

@@

Our results indicated that MaxEnt SDM's were able to provide robust
estimates of climatic suitability for \emph{D. rubiformis} in South
Africa. AUC values greater than 0.80 are typically considered good
fitting models (having high predictive power) (Fielding and Bell, 1997).
When MaxEnt models, calibrated using native-range records for \emph{D.
rubiformis} from Australia, were projected over South Africa, they had
AUC scores of 0.83 - 0.84, indicative of high power to discriminate
between sites where \emph{D. rubiformis} had established in South Africa
or not. Additionally, we showed that the probability that \emph{D.
rubiformis} was recorded at a field site in South Africa increased with
higher MaxEnt climatic suitability scores. This result demonstrates the
usefulness of the MaxEnt SDM and that, at least for our case-study,
SDM's can be transferred into novel geographic regions, and provide
valuable information to guide policy making and the development of
management programmes. For example, biological control programmes such
as the programme in which \emph{D. rubiformis} is used to curtail the
spread of the highly invasive weed \emph{A. mearnsii} expend many
resources (time and money) to mass-rear insect populations that are then
released into the field. The positive correlation between MaxEnt
suitability scores and \emph{D. rubiformis} establishment means that
researchers can develop and implement mass-rearing and experimental
release programmes for the insect that prioritise releasing the insect
at sites that are highly climatically suitable, and thus, more likely
the insect will establish viable populations. This may assist in
improving the level of control over the target weed and increasing the
efficiency of resources expended by increasing the chances of
establishing viable insect populations.

Our study adds to a growing body of literature indicating that SDM model
complexity affects model performance and transferability when being
projected into novel geographic regions. While the default MaxEnt model
had the highest predictive power in the training area (Australia), this
model performed extremely poorly when transferred over South Africa. In
contrast, the four MaxEnt models calibrated with tuned settings showed
high predictive power when transferred. The poor transferability of the
Default model is likely explained by default settings overfitting the
model on the training points (Warren et al., 2014). This finding
corroborates other studies showing that high predictive power in the
model training area is not a guarantee of transferability (Duque-Lazo et
al., 2016; Warren et al., 2014). We echo that recommendations of
Shcheglovitova and Anderson (2013) and Muscarella et al. (2014) that
model tuning should be performed to estimate optimal model complexity
when transferring MaxEnt models in space and/or time in order to
maximise their usefulness.

@@

Species distribution models are becoming increasingly popular with
researchers, stakeholders, policy makers and land managers alike,
particularly for making predictions in novel geographic geographic
regions or forecasting species responses to climate change. Transfering
SDM's in space and/or time, however, has been met with justifiable
resilience and concerns over how well these models perform upon
transfer. In this study, we presented a case-study demonstrating that
MaxEnt SDM's were able to accurately predict the distribution of an
Australian insect when introduced into South Africa. Our study is one of
only a few studies to date validating MaxEnt models using spatially
independent data. However, the accuracy of the MaxEnt models was
dependent on the settings used to calibrate the models, with default
MaxEnt programme settings having low predictive power. Our results
demonstrate that MaxEnt can be useful in predicting where a species may
establish, even when projected into a novel geographic area, but that
users need to be aware of how model settings can influence model outputs
and usefulness. Demonstrating how SDM's can be useful, while
communicating uncertainty in their predictions and outputs, is essential
for building confidence in the use of SDM's (Blasi et al.~2020). We
showed how validating predictive models can be used to guide the
implementation of a biological control programme by optimising the
redistribution and release of \emph{D. rubiformis} in geographic areas
that are climatically suitable and where the probability of the insect
establishing is greater than 50\%.

@@

@@

@@

@@

@@

@@

@@

\begin{ThreePartTable}
\begin{TableNotes}
\item[a] Adjusted to indicate change in Y for each 1\% unit increase in covariate
\end{TableNotes}
\begin{longtable}[l]{lllll}
\toprule
Model & $\beta$\textsuperscript{a} & $\chi$\textsubscript{2} & d.f. & \textit{P}\\
\midrule
\endfirsthead
\multicolumn{5}{@{}l}{\textit{(continued)}}\\
\toprule
Model & $\beta$\textsuperscript{a} & $\chi$\textsubscript{2} & d.f. & \textit{P}\\
\midrule
\endhead

\endfoot
\bottomrule
\insertTableNotes
\endlastfoot
\cellcolor{gray!6}{Default settings} & \cellcolor{gray!6}{1.02} & \cellcolor{gray!6}{1.77} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{0.18}\\
AUCtest & 1.07 & 13.00 & 1 & < 0.001\\
\cellcolor{gray!6}{AUCdiff} & \cellcolor{gray!6}{1.14} & \cellcolor{gray!6}{14.95} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{< 0.001}\\
OR10 & 1.10 & 14.38 & 1 & < 0.001\\
\cellcolor{gray!6}{AICc} & \cellcolor{gray!6}{1.09} & \cellcolor{gray!6}{14.38} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{< 0.001}\\*
\end{longtable}
\end{ThreePartTable}

@@

\begin{longtable}[l]{llllll}
\toprule
Model & RM & FC & AUC\textsubscript{test} & AUC\textsubscript{diff} & OR\textsubscript{10}\\
\midrule
\endfirsthead
\multicolumn{6}{@{}l}{\textit{(continued)}}\\
\toprule
Model & RM & FC & AUC\textsubscript{test} & AUC\textsubscript{diff} & OR\textsubscript{10}\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{Default} & \cellcolor{gray!6}{1.0} & \cellcolor{gray!6}{HLQPT} & \cellcolor{gray!6}{0.94} & \cellcolor{gray!6}{0.03} & \cellcolor{gray!6}{0.15}\\
AUCtest & 1.5 & HLQPT & 0.95 & 0.02 & 0.15\\
\cellcolor{gray!6}{AUCdiff} & \cellcolor{gray!6}{4.0} & \cellcolor{gray!6}{HLQPT} & \cellcolor{gray!6}{0.94} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{0.14}\\
OR10 & 6.0 & HLQ & 0.92 & 0.02 & 0.10\\
\cellcolor{gray!6}{AICc} & \cellcolor{gray!6}{4.0} & \cellcolor{gray!6}{H} & \cellcolor{gray!6}{0.94} & \cellcolor{gray!6}{0.02} & \cellcolor{gray!6}{0.12}\\*
\end{longtable}

>>>>

\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

@@

Ecological models are important tools to support and guide the
development and implementation of environmental policies and management
programs. Species distributions models (SDM's), such as the popular
MaxEnt software, are frequently used to guide conservation programmes,
predict the potential distribution of invasive species, forecast the
impacts of climate change and develop applied ecological research
(e.g.~biological control). Many applications of these models require
that SDM's are transferred in either space and/or time. However, few
studies to date have tested the transferability, and thus usefulness, of
MaxEnt models using fully independent data. Moreover, numerous authors
have raised concerns over how model complexity (controlled primarily by
feature class and regularisation multiplier settings) may affect MaxEnt
model transferability. In this paper, we evaluated the usefulness of
MaxEnt models transferred in space using a native Australian insect,
\emph{Dasineura rubiformis} Kolesik (Diptera: Cecidomyiidae) that has
been intentionally introduced as a biological control agent of the
invasive plant, \emph{Acacia mearnsii} De Wild (Fabaceae) in South
Africa. MaxEnt models were developed using native-range records only
(Australia) and projected over South Africa to identify the potential
climatic suitability for the insect, using a range of model settings
configurations. Model transferability was assessed using independent
post-release data from South Africa. Our results demonstrated that
MaxEnt scores were positively correlated with increased establishment
rates for \emph{D. rubiformis} in South Africa. MaxEnt model outputs and
projections were relatively consistent, irrespective of the settings
used. Despite MaxEnt having to extrapolate over much of South Africa,
MaxEnt performance was higher than modelling climatic suitability as a
function of whether models were in extrapolation or interpolation. Our
study demonstrates that MaxEnt models can prove useful when transferred
in space, however, users need to be aware of the effect of different
model settings configurations and model extrapolation can have on model
transferability and usefulness in applied ecological settings.

@@

Spatial autocorrelation is an important factor that may affect model
outputs. Filtering of species occurrence data may limit the inherent
biases in the data and improve model quality (Veloz, 2009). To avoid
pseudo-replication, only one occurrence record per 2.5 minute grid cell
was used for model calibration. Species occurrence datasets were thinned
using the \texttt{spThin} package (Aiello-Lammens et al., 2015), and
spatial autocorrelation analyses were performed using the
\texttt{ecospat} package (Di Cola et al., 2017).

@@

Climate data were obtained by downloading the standard set of 19
bioclimatic variables from the WorldClim ver. 1.4 database (Hijmans et
al., 2005)\\
(data available at: www.worldclim.org/download.html). This dataset is
representative of annual and seasonal means and variation of temperature
and precipitation metrics averaged over the 1950--2000 time period
(current climate) at a 5 arc minute resolution.

@@

Five candidate MaxEnt models were developed using native-range
(Australia) training data for \emph{D. rubiformis}. The five models
differed in the feature classes and regularisation multiplier settings
used by MaxEnt to build the models. The five models were specified with
(1) default MaxEnt settings, and four optimised settings configurations
that (2) maximised model performance based on AUC\textsubscript{test},
(3) AUC\textsubscript{diff}, (4) OR\textsubscript{10} and (5) AICc
(Table S1). The AUC values for these five models ranged between 0.89 -
0.92, depending on the MaxEnt settings configuration used. As such, all
five candidate models were considered useful and had high predictive
accuracy in distinguishing between \emph{D. rubiformis} recorded
presences and background points in its native range. While default
MaxEnt settings produced high discriminatory power when tested in the
training area of Australia (AUC = 0.89), models calibrated with tuned
settings configurations led to less overfitting (lower
AUC\textsubscript{diff}), better omission rates (best approximated the
expectation for OR\textsubscript{10}), and more parsimonious models
(AICc) (Fig. 2).

\hypertarget{model-performance}{%
\subsection{3.2. Model performance}\label{model-performance}}

When evaluated on independent testing data in South Africa, the MaxEnt
models showed relatively high predictive accuracy, irrespective of the
MaxEnt settings used to calibrate the model. For all models, the
probability that \emph{D. rubiformis} was recorded at a field site in
South Africa increased with higher MaxEnt climatic suitability scores
(Fig. 3). All five MaxEnt models demonstrated a statistically
significant positive relationship between MaxEnt suitability scores and
the probability of \emph{D. rubiformis} establishment in South Africa
(Table. 1), and high power to discriminate between sites where \emph{D.
rubiformis} had established or not (AUC: 0.79 - 0.91) (Fig. 4). The
predicted climatic suitability for \emph{D. rubiformis} across South
Africa did vary somewhat depending on the MaxEnt settings used to
calibrate the model (Fig. 5). All MaxEnt models predicted relatively
high climatic suitability for \emph{D. rubiformis} in the far south-west
of South Africa and in the southern Cape region. However, the four
MaxEnt models calibrated with tuned model settings differed from the
default settings model by predicting climatic suitability for \emph{D.
rubiformis} along the entire south and east Coast of South Africa.

Despite the high performance of the MaxEnt models when transferred in
space, MESS maps indicated that the MaxEnt models were extrapolating
climatic suitability scores for \emph{D. rubiformis} over the vast
majority of South Africa (Fig. 6a). Indeed, 54 of the 78 field sites
surveyed for \emph{D. rubiformis} in South Africa occur in geographic
regions where the MaxEnt models were extrapolating. \emph{Dasineura
rubiformis} established at 23 of 24 sites in interpolation (96\%), while
it established at 44 of 54 sites in extrapolation (82\%) (Fig. 6b). We
found no evidence that a site being in extrapolation/interpolation was a
statistically significant predictor of \emph{D. rubiformis}
establishment in South Africa (X\textsubscript{2} = 3.40, d.f = 1,
\emph{P} = 0.07). Moreover, classifying sites as being in
extrapolation/interpolation yielded lower power to discriminate between
sites where \emph{D. rubiformis} had established or not (AUC: 0.63) than
all of the MaxEnt models.

@@

Our results indicated that MaxEnt SDM's were able to provide robust
estimates of climatic suitability for \emph{D. rubiformis} in South
Africa. AUC values greater than 0.75 are typically considered good
fitting models (having high predictive power) (Fielding and Bell, 1997).
When MaxEnt models, calibrated using native-range records for \emph{D.
rubiformis} from Australia, were projected over South Africa, they had
AUC scores of 0.89 - 0.92, indicative of high power to discriminate
between sites where \emph{D. rubiformis} had established in South Africa
or not. Additionally, we showed that the probability that \emph{D.
rubiformis} was recorded at a field site in South Africa increased with
higher MaxEnt climatic suitability scores. This result demonstrates the
usefulness of the MaxEnt SDM and that, at least for our case-study,
SDM's can be transferred into novel geographic regions, and provide
valuable information to guide policy making and the development of
management programmes. For example, biological control programmes such
as the programme in which \emph{D. rubiformis} is used to curtail the
spread of the highly invasive weed \emph{A. mearnsii} expend many
resources (time and money) to mass-rear insect populations that are then
released into the field. The positive correlation between MaxEnt
suitability scores and \emph{D. rubiformis} establishment means that
researchers can develop and implement mass-rearing and experimental
release programmes for the insect that prioritise releasing the insect
at sites that are highly climatically suitable, and thus, more likely
the insect will establish viable populations. This may assist in
improving the level of control over the target weed and increasing the
efficiency of resources expended by increasing the chances of
establishing viable insect populations.

Our study adds to a growing body of literature indicating that SDM model
complexity affects model performance and transferability when being
projected into novel geographic regions. While the default MaxEnt model
had the high predictive power in the training area (Australia), this
model was somewhat overfit to the training data (Warren et al., 2014).
This finding corroborates other studies showing that high predictive
power in the model training area is not a guarantee of transferability
(Duque-Lazo et al., 2016; Warren et al., 2014). We echo that
recommendations of Shcheglovitova and Anderson (2013) and Muscarella et
al. (2014) that model tuning should be performed to estimate optimal
model complexity when transferring MaxEnt models in space and/or time in
order to maximise their usefulness.

@@

Species distribution models are becoming increasingly popular with
researchers, stakeholders, policy makers and land managers alike,
particularly for making predictions in novel geographic geographic
regions or forecasting species responses to climate change. Transfering
SDM's in space and/or time, however, has been met with justifiable
resilience and concerns over how well these models perform upon
transfer. In this study, we presented a case-study demonstrating that
MaxEnt SDM's were able to accurately predict the distribution of an
Australian insect when introduced into South Africa. Our study is one of
only a few studies to date validating MaxEnt models using spatially
independent data. However, the accuracy of the MaxEnt models and their
climatic suitability projections were dependent on the settings used to
calibrate the models. Our results demonstrate that MaxEnt can be useful
in predicting where a species may establish, even when projected into a
novel geographic area, but that users need to be aware of how model
settings and model extrapolation can influence model outputs and
usefulness. Demonstrating how SDM's can be useful, while communicating
uncertainty in their predictions and outputs, is essential for building
confidence in the use of SDM's (Blasi et al.~2020). We showed how
validating predictive models can be used to guide the implementation of
a biological control programme by optimising the redistribution and
release of \emph{D. rubiformis} in geographic areas that are
climatically suitable and where the probability of the insect
establishing is greater than 50\%.

@@

\includegraphics{C:/Users/s1900332/OneDrive - Rhodes University/Manuscripts/MS-Dasinuera-MaxEnt-Transfer/./ms_body/ms_figs/fig_1_distributions.png}

@@

\includegraphics{C:/Users/s1900332/OneDrive - Rhodes University/Manuscripts/MS-Dasinuera-MaxEnt-Transfer/./ms_body/ms_figs/fig_2_model_tuning.png}

@@

\includegraphics{C:/Users/s1900332/OneDrive - Rhodes University/Manuscripts/MS-Dasinuera-MaxEnt-Transfer/./ms_body/ms_figs/fig_3_logits.png}

@@

\includegraphics{C:/Users/s1900332/OneDrive - Rhodes University/Manuscripts/MS-Dasinuera-MaxEnt-Transfer/./ms_body/ms_figs/fig_4_auc.png}

@@

\includegraphics{C:/Users/s1900332/OneDrive - Rhodes University/Manuscripts/MS-Dasinuera-MaxEnt-Transfer/./ms_body/ms_figs/fig_5_maxent_maps.png}

@@

\includegraphics{C:/Users/s1900332/OneDrive - Rhodes University/Manuscripts/MS-Dasinuera-MaxEnt-Transfer/./ms_body/ms_figs/fig_6_mess.png}

@@

\begin{ThreePartTable}
\begin{TableNotes}
\item[a] Adjusted to indicate change in Y for each 1\% unit increase in climatic similarity
\end{TableNotes}
\begin{longtable}[l]{lllll}
\toprule
Model & $\beta$\textsuperscript{a} & $\chi$\textsubscript{2} & d.f. & \textit{P}\\
\midrule
\endfirsthead
\multicolumn{5}{@{}l}{\textit{(continued)}}\\
\toprule
Model & $\beta$\textsuperscript{a} & $\chi$\textsubscript{2} & d.f. & \textit{P}\\
\midrule
\endhead

\endfoot
\bottomrule
\insertTableNotes
\endlastfoot
\cellcolor{gray!6}{Default settings} & \cellcolor{gray!6}{1.11} & \cellcolor{gray!6}{26.21} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{< 0.001}\\
AUCtest & 1.04 & 17.50 & 1 & < 0.001\\
\cellcolor{gray!6}{AUCdiff} & \cellcolor{gray!6}{1.03} & \cellcolor{gray!6}{12.29} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{< 0.001}\\
OR10 & 1.02 & 9.01 & 1 & 0.003\\
\cellcolor{gray!6}{AICc} & \cellcolor{gray!6}{1.04} & \cellcolor{gray!6}{16.21} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{< 0.001}\\*
\end{longtable}
\end{ThreePartTable}

@@

\begin{longtable}[l]{lllllll}
\toprule
Model & RM & FC & AUC\textsubscript{test} & AUC\textsubscript{diff} & OR\textsubscript{10} & AIC\textsubscript{c}\\
\midrule
\endfirsthead
\multicolumn{7}{@{}l}{\textit{(continued)}}\\
\toprule
Model & RM & FC & AUC\textsubscript{test} & AUC\textsubscript{diff} & OR\textsubscript{10} & AIC\textsubscript{c}\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\cellcolor{gray!6}{Default} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{HLQPT} & \cellcolor{gray!6}{0.89} & \cellcolor{gray!6}{0.04} & \cellcolor{gray!6}{0.18} & \cellcolor{gray!6}{564.46}\\
AUCtest & 6 & H & 0.89 & 0.02 & 0.09 & 15.56\\
\cellcolor{gray!6}{AUCdiff} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{HLQPT} & \cellcolor{gray!6}{0.89} & \cellcolor{gray!6}{0.02} & \cellcolor{gray!6}{0.13} & \cellcolor{gray!6}{485.91}\\
OR10 & 6 & HLQPT & 0.92 & 0.02 & 0.12 & 144.39\\
\cellcolor{gray!6}{AICc} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{H} & \cellcolor{gray!6}{0.90} & \cellcolor{gray!6}{0.02} & \cellcolor{gray!6}{0.09} & \cellcolor{gray!6}{0.00}\\*
\end{longtable}
